Progress with the NOSAMS<br>Hybrid Gas Ion Source

### 2021-05-03 doc/SNEAP2021/SNEAP2021_HGIS_presentation/SNEAP2021_HGIS_presentation.Rmd
Minor edits

.pull-left[
### Goal:

* Maximize gas density and residence time where sputtering and ionization are happening.

### Potential for:

@@

Increase CO<sub>2</sub> flow by increasing pCO<sub>2</sub>:
* Add CO<sub>2</sub> 
* Reduce volume

Gas mixtures - helium dilution:
* Increase pressure and total flow
* Reduce pCO<sub>2</sub>
* CO<sub>2</sub> flow remains constant? No - viscosity
* He is 25% more viscous than CO<sub>2</sub>
]

@@

### Flow control
* Change volume
* Add CO<sub>2</sub>
* Add helium

### For a given sample size:
* High inlet volume = low inlet pressure (NEC inlet)
* Low inlet volume = high inlet pressure (Ionplus inlet)

@@

Helium displacement of CO<sub>2</sub> from vial. Monitor currents and ratios as pCO<sub>2</sub> decreases.

@@

.pull-left[
#### Modeled blank:
* Fm: `r format(blank_val$Fm_blank, digits = 3)`
* Current: `r format(blank_val$m_blank, digits = 3)` μA
]

.pull-right[
#### Measured blank:
* Fm: `r ds %>% filter(Gas == "Blank") %>% pull(mean) %>% mean() %>% format(digits = 3)`
* Current: `r ds %>% filter(Gas == "Blank") %>% pull(Cur) %>% mean() %>% format(digits = 3)` μA
]
]

@@

.pull-left[
If **standards**, **blanks**, and **unknowns** have the **same** blank and current:

### Linear fit used to correct:

@@

* Currents > 2 μA
* Note current dependence

@@

NOSAMS has developed a successful method for analyzing radiocarbon in carbonates with an open-split interface delivering CO<sub>2</sub> gas to a NEC MCSNICS gas-accepting cesium sputter ion source.

>>>>

.pull-left[
### Goal

* Maximize gas density and residence time where sputtering and ionization are happening

### Potential for

@@

#### Increase CO<sub>2</sub> flow by increasing pCO<sub>2</sub>
* Add CO<sub>2</sub> 
* Reduce volume

#### Gas mixtures - helium dilution
* Increase pressure and total flow
* Reduce pCO<sub>2</sub>
* CO<sub>2</sub> flow remains constant? No - viscosity
* He is 25% more viscous than CO<sub>2</sub>
]

@@

#### Flow control
* Change volume
* Add CO<sub>2</sub>
* Add helium

#### For a given sample size
* High inlet volume = low inlet pressure (NEC inlet)
* Low inlet volume = high inlet pressure (Ionplus inlet)

@@

Helium displacement of CO<sub>2</sub> from vial.

Monitor currents and ratios as pCO<sub>2</sub> decreases.

@@

.pull-left[
#### Modeled blank
* Fm: `r format(blank_val$Fm_blank, digits = 3)`
* Current: `r format(blank_val$m_blank, digits = 3)` μA
]

.pull-right[
#### Measured blank
* Fm: `r ds %>% filter(Gas == "Blank") %>% pull(mean) %>% mean() %>% format(digits = 3)`
* Current: `r ds %>% filter(Gas == "Blank") %>% pull(Cur) %>% mean() %>% format(digits = 3)` μA
]
]

@@

.pull-left[
If **standards**, **blanks**, and **unknowns** have the **same** blank and current, current drops out.

#### Linear fit used to correct:

@@

* Currents > 2 μA
* Current dependence
* Underestimation of error

@@

**NOSAMS has developed a successful method for analyzing radiocarbon in carbonates with an open-split interface delivering CO<sub>2</sub> gas to a NEC MCSNICS gas-accepting cesium sputter ion source.**
